Think deep for reef resilience

### 2025-08-15 paper/paper_draft.qmd
Update mistake in the cluster labelling timeperiod details

To identify groups of reefs that are resilient, intermediate, and non-resilient, we
clustered reefs into three clusters based on their temporal behaviour as indicated by coral
cover over time, using timeseries from 2025-2075. The Complexity-Invariant Distance (CID)
between each timeseries was calculated to identify timeseries that behave similarly
[@batista2014]. The CID corrects the Euclidean distance between pairs of timeseries (which
accounts for magnitude differences) with the complexity of each timeseries (obtained through
a measure of their variability) to ensure reefs are clustered based on their underlying
temporal dynamics rather than simply their average coral cover. The process creates a
distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that
is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The three reef
clusters are assigned a qualitative level from "low", "medium" and "high" based on their
relative median timeseries over the 2030-2050 period. Assigning cluster labels based on this
period prevents cluster labels being assigned during the steeply declining period from
2025-2030 and during the post-2050 period when many reefs have cover below 5% of their area.

>>>>

To identify groups of reefs that are resilient, intermediate, and non-resilient, we
clustered reefs into three clusters based on their temporal behaviour as indicated by coral
cover over time, using timeseries from 2025-2075. The Complexity-Invariant Distance (CID)
between each timeseries was calculated to identify timeseries that behave similarly
[@batista2014]. The CID corrects the Euclidean distance between pairs of timeseries (which
accounts for magnitude differences) with the complexity of each timeseries (obtained through
a measure of their variability) to ensure reefs are clustered based on their underlying
temporal dynamics rather than simply their average coral cover. The process creates a
distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that
is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The three reef
clusters are assigned a qualitative level from "low", "medium" and "high" based on their
relative median timeseries over the 2030-2060 period. Assigning cluster labels based on this
period prevents cluster labels being assigned during the steeply declining period from
2025-2030 and during the post-2060 period when many reefs have cover below 5% of their area.
